Draft

### 2017-08-26 Thesis/Draft.tex
Update APT section

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Draft},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Draft}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Tim Radtke}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{5/28/2017}

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage[lined,boxed]{algorithm2e}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}

@@

\section{Introduction to Sequential Sampling and Multi-Armed
Bandits}\label{introduction-to-sequential-sampling-and-multi-armed-bandits}

@@

The problem of best arm identification is very related to statistical
hypothesis testing as noted by Chernoff (1958) since in the end, one has
to make a decision about how the means of distributions relate to each
other. The main difference of course being that the sampling procedure
becomes integrated into the evaluation of the distributions. Given the
focus on exploration, the problem is usually described with a loss
function different from cumulative regret. Audibert et al. (2010)
introduce a soft measure called \emph{simple regret} based on which they
describe UCB policies. Other authors investigate hard, binary measures
that are equal to 1 when the best arm has not been identified (Russo,
2016; Garivier and Kaufmann, 2016).

The problem of best arm identification can readily be extended to the so
called Top-\(m\) problem of identifying the best \(m\) of \(K\) arms.

\begin{itemize}
\item
  Chernoff -\textgreater{} Sequential Sampling; as mentioned by Russo;
  Garivier and Kaufmann
\item
  Thompson
\item
  Optimality for Stochastic Cumulative Regret
\item
  UCB, KL-UCB, Thompson Sampling
\end{itemize}

-\textgreater{} Many variations: Infinite-armed, adversarial, dueling

\begin{itemize}
\item
  Best Arm Identification
\item
  Top-\(m\) Identification
\item
  Thresholding Bandit Problem
\item
  Maybe an example?
\end{itemize}

@@

\section{Thresholding Bandit Problem}\label{thresholding-bandit-problem}

The \emph{Thresholding Bandit Problem} described in Locatelli et al.
(2016) can be considered a variant of a variant. It can be framed inside
of the wider literature of \emph{Pure Exploration} multi-armed bandit
problems. In particular, it shares characteristics with the
\emph{Top-\(m\)} problem. This problem is concerned with finding the
\(m\) best arms as described by the means of their corresponding
distributions. This in turn is similar to the \emph{combinatorial
bandit} problem, which also aims at finding the \(m\) best arms.
However, it is able to pull several arms at once: Think of an online
shop that shows five recommended products on a product detail page.
These five recommended products might each be represented by an arm, and
we look for the products with the largest mean conversion rate. The
thresholding bandit problem we discuss here, however, is concerned with
pulling a single arm at a time. And so a more appropriate situation is
that of a website presenting a banner. Again, think of an online shop
trying to promote a certain category. The content team came up with a
number of different designs for the banner, and it's not clear how many
click-throughs they will gather.

The idea now is that we would like to classify the banners into two
distinct groups: A group with mean conversion rates \(\mu_i\) below
threshold \(\tau\), and a group with mean conversion rates \(\mu_i\)
above threshold \(\tau\). This might be the optimization problem when we
are concerned with not falling below a certain minimum level
click-through rate with the banners we're choosing.

If it turns out that in general we can find relatively quickly whether
arms are above or below a threshold, then this kind of test can be used
to safeguard against very bad versions in a test. Before we move to a
Top-\(m\) test, we might want to run a thresholding version and then
continue only with the arms classified into the group above the
threshold. This might be justified when adjusting parts of the checkout
process of an online shop, where the conversion rate or the average
order value should not drop below a threshold.

\subsection{Setup}\label{setup}

In any case, the problem boils down to the following. As usual in
multi-armed bandit problems, we have \(K\) arms
\(\mathcal{A} = \{1, \dots K\}\). We can pull arm \(k\) at time \(t\) to
collect feedback in form of the random variable \(X_{k,t}\) which is
distributed according to the arm's distribution \(\nu_k\). In general,
we are concerned with estimating for each arm \(i\) the mean \(\mu_i\)
of its distribution \(\nu_i\). In contrast to most bandit problems,
however, we do not directly compare arms with each other by comparing
their means. That would for example be the case for pure exploration
bandits, where it is necessary to compare the arms because one aims to
find the best one relative to the others. In the case of the
thresholding bandit, however, we compare each arm's mean \(\mu_i\)
individually against the threshold \(\tau \in \mathbb{R}\) which is
known and fixed before the experiment. One might compare this to a pure
exploration bandit in which the mean of the best arm is known upfront.
We will see later that this fact leads to advantages in the design of
algorithms which are not as readily available in other bandit settings.

In Locatelli (2016), the arms' distributions are assumed to follow an
\(R\)-sub-Gaussian distribution. Under this assumption, the authors are
able to proof a general lower bound as well as an algorithm with a
matching upper bound. Both hinge upon the \emph{complexity} of a given
problem. Since bandit problems can differ in the number of the arms
\(K\) and the means of each arm, some pose easier identification
problems than others. Indeed, in the thresholding problem, the
difficulty of the problem naturally depends on how close (the means of
the) distributions are to the fixed threshold. Intuitively, the closer a
mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it is to
distinguish the two successfully based on samples from the distribution
\(\nu_i\). A straightforward measure of this distance is given by
\(\Delta_i = |\tau - \mu_i| + \epsilon\), where \(\epsilon\) defines a
\(2\epsilon\) interval around the threshold \(\tau\) in which we allow
ourselves to make a mistake at no cost. In the case of sub-Gaussian
distributions, this distance is not only simple but can be interpreted
very naturally as we will come to understand later.

If we extend this idea to the set of arms \(i \in \{1,...,K\}\) in a
given bandit problem, a measure of the overall diffulty of the problem,
or the problem's complexity, might be given by
\(H = \sum_{i=1}^{K} \Delta_i^{-2}\). In particular, it shows that just
adding additional arms leads to an increase in complexity (since we need
a larger budget to sample each arm the same number of times as before).
Likewise, a smaller \(\Delta_i\) increases the complexity as arms become
harder to classify. Choosing the complexity measure in this way fits the
distance measure \(\Delta_i\) and turn out to be useful in the proof of
an upper bound for the APT algorithm presented in Locatelli et al.
(2016).

We also see that this definition may lose relevancy as we move away from
\(R\)-sub-Gaussian distributions. (ADD QUICK EXAMPLE OF WHAT CHANGES;
REFER TO LATER PART AND DESCRIBE THIS AS THE MOTIVATION OF THE PAPER)

Another characteristic uniquely identifying bandit problems is the
regret measure that we aim to optimize. As explained during the
introduction, multi-armed bandits traditionally optimize cumulative
regret. The notion of regret considered in the thresholding bandit,
however, is more akin to the simple regret in pure exploration bandits
or the error probability in sequential hypothesis testing. Indeed, one
can most easily describe the regret in the thresholding case as the
probability of misclassifying any arm. Or, more rigorously, define the
set of all arms with mean larger than the threshold,
\(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
Consequently,
\(\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}\). At the end
of the sampling rule/procedure (!!we have not mentioned yet the fact
that we're in the fixed budget case!!), we demand that any algorithm
returns the two corresponding \emph{estimated} sets:
\(\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}\),
as well as
\(\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}\).
We simply demand an answer to the question which arms have means above
the threshold \(/tau\), and which arms lie below \(\tau\). Let \(T\) be
the overall number of samples the algorithm is allowed to pull. We
define the loss as
\(\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}\).
That is, we compare the return set with the true set and collect a loss
of 1 if any arm with a true mean outside the \(2\epsilon\) interval
around \(\tau\) was misclassified. It is important to realize that arms
with means inside the \(2 \epsilon\) interval may be misclassified
without it affecting the loss. These arms are considered close enough to
the threshold that we do not care whether they lie above or below.

ADD A GRAPHIC THAT VISUALIZES THE ESTIMATED AND THE REQUIRED RETURN SETS

Now, the expected regret/loss is defined as
\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))\).
This, of course, is the mentioned probability of making a mistake.

Lastly, it is to mention that we are considering the fixed-budget
version of the thresholding bandit problem. We thus fix the number of
samples that the algorithm will pull upfront at \(T\). The task of the
algorithm is then to find a sampling rule or strategy which distributes
the budget \(T\) among the \(K\) arms in such a way that the expected
regret, or the error probability, is minimized. In other terms, the
algorithm aims to use the \(T\) samples in a way that lets him return
the two sets \(\hat{\mathcal{S}}_{\tau}\) and
\(\hat{\mathcal{S}}_{\tau}^C\) with as much confidence as possible. This
again shows the contrast to the fixed confidence setting in which one
fixes the confidence level upfront and lets the algorithm draw as many
samples as necessary to reach the required confidence.

At this point, we have defined the fixed budget thresholding bandit
setup for any algorithm in the case of sub-Gaussian distributions. We
thus proceed to describe the APT algorithm proposed in Locatelli et al.
(2016).

\subsection{The APT Algorithm}\label{the-apt-algorithm}

@@

\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
\Input{$\tau$, $\epsilon$}
\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
\BlankLine
\emph{Pull each arm once}\;
\For{$t = K+1$ \KwTo $T$}{
  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} \sqrt{|\hat{\mu}_i(t) - \tau|+\epsilon}$}\;
  \emph{Observe reward $X \sim \nu_{I_t}$}\;
}
\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{algo_apt}
\end{algorithm}

@@

In the following we describe the \emph{Anytime Parameter-free
Thresholding} (APT) algorithm proposed in Locatelli et al. (2016), which
is a simple yet effective algorithm and displays some very favorable
characteristics when compared with alternative algorithms.

From the general setup, we already know how the algorithm will end.
After it has drawn \(T\) samples, the algorithm makes a decision of
which arms to include in the return sets on basis of the empirical means
\(\hat{\mu}_i(T)\) estimated based on the samples drawn until time
\(T\). Furthermore, the threshold and interval around the threshold are
fixed upfront and serve as argument to the algorithm:
\((\tau, \epsilon)\). For a given arm \(i\) and a given time \(t\), we
let \(T_i(t)\) represent the number of samples drawn from arm \(i\)
until time \(t\) (including). Consequently, the empirical mean of arm
\(i\) at time \(t\) is given by
\(\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
arm is pulled for the \(s\)-th time.

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Draft},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Draft}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{hyperref}
\usepackage[lined,boxed]{algorithm2e}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}

@@

\section{\texorpdfstring{Introduction
\label{chap:Introduction}}{Introduction }}\label{introduction}

@@

The problem of best arm identification is very related to statistical
hypothesis testing as noted by Chernoff (1958) since in the end, one has
to make a decision about how the means of distributions relate to each
other. The main difference of course being that the sampling procedure
becomes integrated into the evaluation of the distributions. Given the
focus on exploration, the problem is usually described with a loss
function different from cumulative regret. Audibert et al. (2010)
introduce a soft measure called \emph{simple regret} based on which they
describe UCB policies. Other authors investigate hard, binary measures
that are equal to 1 when the best arm has not been identified (Russo,
2016; Garivier and Kaufmann, 2016). These binary measures correspond to
the probability of the identified arm being the best, and thus
inherently related to hypothesis testing. The problem of best arm
identification can readily be extended to the so called Top-\(m\)
problem of identifying the best \(m\) of \(K\) arms (Kaufmann and
Kalyanakrishnan, 2013; Kaufmann et al. 2016).

In this thesis, we consider the thresholding bandit problem. Instead of
identifying the best \(m\) out of \(K\) arms, one aims to find all out
of \(K\) distributions that have a mean larger than a threshold fixed
upfront. In the form described in Locatelli et al. (2016), algorithms in
the thresholding bandit problem are evaluated against a binary loss
function penalizing whenever an arm has not been classified correctly as
being above the threshold and thus focus on exploration similar to
algorithms employed for best arm identification. Indeed, Locatelli et
al. (2016) show how their thresholding algorithm can be used for best
arm identification when the mean of the best arm is known upfront.

In the following, we first present the thresholding bandit problem in
detail. To then extend upon the algorithm proposed by Locatelli et al.
(2016), we first explore how the Kullback-Leibler divergence has been
employed in the best arm identification literature by Garivier and
Kaufmann (2016) and Kaufmann et al. (2016). We shortly describe two
variance based algorithms for the thresholding bandit problem introduced
in Mukherjee et al. (2017) and Zhang et al. (2017), before introducing
the new Simple Likelihood Ratio algorithm. We end with experiments to
examine the performance of different algorithms.

@@

\section{\texorpdfstring{Thresholding Bandit Problem
\label{chap:ThresholdingBanditProblem}}{Thresholding Bandit Problem }}\label{thresholding-bandit-problem}

To introduce the thresholding bandit problem, consider a game in which
the learner is tasked to find those slot machines within a row of \(K\)
slot machines in a casino that give a mean payoff larger than a fixed
threshold \(\tau\), for example \(\tau = 0\). The learner cannot pull
all slot machines at the same time. Instead, he acquires samples
sequentially from one slot machine at a time to learn about their payoff
structure. The learner has a budget of \(T\) slot machine pulls. After
\(t-1\) samples, the learner has observed \(T_i(t-1)\) samples from slot
machine \(i\). The payoffs \(X_{i,1}, ..., X_{i,T_i(t-1)}\) are drawn
from the payoff distribution \(\nu_i\) underlying the slot machine
\(i\). At time \(t\), the learner considers the payoffs he observed so
far in order to choose the next slot machine he would like to pull. His
decision is lead by the goal to classify the slot machines with
distribution \(\nu_i\) and mean payoff
\(\mu_i = \mathbb{E}_{X \sim \nu_i}[X]\) after \(T\) samples as being
above or below the threshold with error probability as small as
possible.

The thresholding bandit problem can thus be framed in the wide
literature on sequential sampling strategies. While its name is
reminiscient of the multi-armed bandit setting, the thresholding bandit
problem is more akin to best arm identification and Top-\(m\)
identification problems due to its focus on exploration: While the
classical multi-armed bandit problems are concerned with cumulative
regret which increases \emph{during} sampling, best arm identification
and thresholding bandits collect loss only once \emph{after} the
sampling procedure (compare Garivier and Kaufmann, 2016; Kaufmann et
al., 2016; Kaufmann and Kalyanakrishnan, 2013). Furthermore, as there
arises an implicit threshold between the means of the \(m\)-th best arm
and the \(m+1\)-th best arm (Kaufmann et al., 2016; Kaufmann and
Kalyanakrishnan, 2013), algorithms for the Top-\(m\) identification
problem classify arms at least implicitly as being above or below a
threshold. The two settings are thus very related.

\subsection{\texorpdfstring{Setup
\label{sec:Setup}}{Setup }}\label{setup}

Consider a setting with a set of \(\mathbb{A}=\{1, ..., K\}\) unknown
probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
idea of multi-armed bandits, we call those distributions arms, and
observations from those arms rewards (Bubeck and Cesa-Bianchi, 2012).
The learner is interested in learning about the structure of the arms;
in particular, he would like to estimate the means \(\mu_1, ..., \mu_K\)
by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from each
arm. However, at time \(t\) the learner cannot observe a reward from
every distribution but must select a single arm \(I_t\) from which he
would like to observe the reward \(X_{I_t,t}\). An adaptive sampling
strategy makes the decision of which arm to pull usually by computing an
index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number of samples
observed until time \(t\) for arm \(i\), then \(B_i(t)\) is a function
of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for arm
\(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set of
indices can be called strategy (Kaufmann et al., 2012) which makes it
clear that the strategy is adapted as more observations are collected.
Strategies of this kind are also called index policies.

What index proves to be useful is determined by the loss function with
which the decisions of the algorithm are evaluated. While many problems
are concerned with finding the arm with the largest mean \(\mu_i\), in
which algorithms collect loss either cumulatively (Auer and
Cesa-Bianchi, 2012) or once at the end of the sampling (Kaufmann et al.,
2016), the thresholding bandit problem considers a slightly different
loss function. Consider a fixed threshold value \(\tau \in \mathbb{R}\)
and an epsilon interval \(\tau \pm \epsilon\) around the threshold for
\(\epsilon \geq 0\). As mentioned in the introduction, the learner is
tasked with classifying arms as having a mean \(\mu_i\) larger or
smaller than \(\tau\). To describe which arms are above the threshold,
we introduce the following set notation (compare Locatelli et al.,
2016): Let \(\mathcal{S}_{\tau}\) be the set of distributions in
\(mathbb{A}\) with mean larger than the threshold:
\(\mathcal{S}_{\tau} := \{i \in \mathbb{A}, \mu_i \geq \tau\}\).
Consequently, the complement is given by the arms with mean below the
threshold,
\(\mathcal{S}^C_{\tau} := \{i \in \mathbb{A}, \mu_i < \tau\}\).

The thresholding problem for the learner is now to use a budget of
overall \(T\) samples (or rounds) to explore the different arms. After
this exploration phase, the learner has to return a set of arms that he
believes to have a mean above the threshold. The problem can thus be
described by the threshold \(\tau\) and a precision \(\epsilon\). When
evaluating the classification of the learner, arms with mean inside of
the epsilon interval will not be considered. The learner only has to
distinguish the means from the threshold correctly up to the precision
\(\epsilon\). Thus, the algorithm is not evaluated against
\(\mathcal{S}_{\tau}\) and \(\mathcal{S}^C_{\tau}\), but needs to
distinguish \(\mathcal{S}_{\tau+\epsilon}\) from
\(\mathcal{S}^C_{\tau-\epsilon}\). As in Locatelli et al. (2016),
whenever we say that ``an arm is over the threshold'', we mean that the
mean of the arm is over the threshold.

The learner's classification is returned as the set
\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subset \mathbb{A}\)
after \(T\) rounds; that is, the set of arms estimated to be over the
threshold. The classification is evaluated against the loss given as
(Locatelli et al., 2016):

\[
\mathcal{L}(T) = \mathbbm{1}{(\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)}
\]

In order to perform well, a learner has to identify all arms that are
over the threshold as such, and to not claim arms as being over the
threshold if they actually are below the threshold. Due to the precision
\(\epsilon\), the loss is not influenced by arms which are too close to
the threshold \(\tau\), that is, arms inside of the
\(\tau \pm \epsilon\) interval. If either \(\hat{\mathcal{S}}_{\tau}\)
contains an arm below \((\tau - \epsilon)\), or
\(\hat{\mathcal{S}}^C_{\tau}\) contains an arm above
\((\tau + \epsilon)\), a loss of \(1\) is accrued. Else, all arms
outside the epsilon interval are classified correctly and the loss is
equal to \(0\). In the case of \(\epsilon = 0\), all arms need to be
classified correctly to not endure any loss.

Algorithms for this thresholding problem can be compared based on their
expected loss. Let \(\mathbb{E}\) be the expectation with regard to the
samples \(X_{i,1}, ..., X_{i,T}\) collected by the algorithm. The
expected loss is then given as

\[
\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor(\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big),
\]

which corresponds to the probability of making a wrong classification.
Both the probability of not identifying an arm that is actually over the
threshold, as well as the probability of accepting an arm as over the
threshold when it is not are evaluated. The oracle strategy would
evaluate all arms correctly with an error probability of \(0\)
(Locatelli et al., 2016).

At this point, we have introduced the general thresholding bandit
problem setting which we will use throughout the thesis. The setting
might be extended by different assumptions to make certain algorithms or
bounds feasible. For that reason, Locatelli et al. (2016) assume that
the distributions \(\nu_i, i \in \mathbb{A}\) are \(R\)-sub-Gaussian.
Under this assumption, the authors are able to prove a lower bound on
the largest probability of error of the best algorithm in the setting we
have just introduced, as well as an upper bound on the performance of
their APT algorithm we will introduce in the following chapter. As in
their paper, we define \(R\)-sub-Gaussian and assume it in the
description of their algorithm and bounds:

\begin{definition}[$R$-sub-Gaussian distribution] 
\label{definition:rsubgaussian}
Let $R > 0$. A distribution $\nu$ is $R$-sub-Gaussian if for all $t \in \mathbb{R}$ we have
\begin{equation*}
\mathbb{E}_{X \sim \nu}[\exp(tX - t\mathbb{E}[X])] \leq \exp(R^2t^2/2).
\end{equation*}
\end{definition}

As noted by Locatelli et al. (2016), this ensures that the mean
\(\mu_i\) of the distributions \(\nu_i\) considered in our problem are
finite. \(R\)-sub-Gaussian distributions furthermore offer concentration
inequalities for the concentration of the empirical mean to the true
mean, which makes it possible to deduce the bounds presented by the
authors and repeated below. The family of \(R\)-sub-Gaussian
distributions encompasses Gaussian distributions of variance \(R^2\) for
\(R \in \mathbb{R}\), as well as all bounded distributions, with the
important case of Bernoulli distributions.

Having described the thresholding bandit setting as well as the
assumption of \(R\)-sub-Gaussianity, we can now proceed to describe the
\emph{Anytime Parameter-free Thresholding} (APT) algorithm proposed in
Locatelli et al. (2016) for the thresholding bandit problem.

\subsection{\texorpdfstring{The Anytime Parameter-free Thresholding
Algorithm
\label{sec:TheAPTAlgorithm}}{The Anytime Parameter-free Thresholding Algorithm }}\label{the-anytime-parameter-free-thresholding-algorithm}

In the following we describe the \emph{Anytime Parameter-free
Thresholding} (APT) algorithm proposed in Locatelli et al. (2016), which
is a simple yet effective algorithm and displays some very favorable
characteristics when compared to alternative algorithms.

We fix the threshold \(\tau\) and epsilon interval around the threshold
given by \(\epsilon\) upfront, and supply them as arguments to the
algorithm: \((\tau, \epsilon)\). Based on the general thresholding
problem, we demand that the algorithm draws samples \(X_{i,t}\) for
\(T\) rounds from the distributions \(\nu_i, i\in \mathbb{A}\). For a
given arm \(i\) and a given time \(t\), we let \(T_i(t)\) represent the
number of samples drawn from arm \(i\) until time \(t\) (including).
Consequently, the empirical mean of arm \(i\) at time \(t\) is given by
\(\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
arm is pulled for the \(s\)-th time. In the case of the APT algorithm,
the decision \(\hat{\mathcal{S}}_{\tau}\) is based on the empirical
means \(\hat{\mu}_i(T)\) estimated from the samples drawn up to time
\(T\):
\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).

As we see in algorithm \ref{alg:APT}, the APT algorithm initiates by
pulling each arm once. Then, for each \(t > K\), it calculates for every
arm the values \(T_i(t)\) and \(\hat{\mu}_i(t)\). Based on the empirical
mean, the algorithm computes the estimated gap between the mean and the
threshold as
\(\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon\).
The decision of which arm is sampled next is then based on the value
\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)\): the algorithm pulls arm
\(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\) minimizing this decision
quantity. After overall \(T\) pulls, the algorithm returns the sets
described in the general setup, \(\hat{\mathcal{S}}_{\tau}\) and
\(\hat{\mathcal{S}}^C_{\tau}\).

@@

\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
\Input{$\tau$, $\epsilon$}
\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
\BlankLine
\emph{Pull each arm once}\;
\For{$t = K+1$ \KwTo $T$}{
  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
  \emph{Observe reward $X \sim \nu_{I_t}$}\;
}
\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
\end{algorithm}

@@

Just like the general index policies mentioned in \autoref{sec:Setup},
we see that the APT algorithm adapts its strategy using an index
\(B_i(t+1)\) for each arm that is based entirely on the observations
observed until time \(t\). Given the arm with the smallest index is
pulled at round \(t+1\), we observe that arms that are estimated to be
further away from the threshold \(\tau\) as measured by the absolute
distance to their empirical mean \(\hat{\mu}_i\), \(\hat{\Delta}_i(t)\),
are pulled less often. Intuitively, it is easier to classify arms as
below or above \(\tau\) when their mean is far away from the threshold.
In contrast to the uniform sampling strategy, APT will gather more
evidence for arms which appear to be inherently more difficult to
classify. Likewise, APT tends to pull arms less often which it already
pulled considerably often as measured by \(T_i(t)\). If arm \(i\) has
been pulled more often than arm \(j\), then we should in general be more
confident in its estimated mean and the corresponding distance to the
threshold. If we are confident in \(i\), then it is better to explore
other arms by drawing an observation from arm \(j\). By adapting its
sampling strategy in this way during the sequential sampling process,
the APT algorithm minimizes the probability of error
\(\mathbb{E}[\mathcal{L}(T)]\) after \(T\) samples have been observed.
